---
output: github_document
---
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# stepFMR

<!-- badges: start -->
[![R-CMD-check](https://github.com/jacksonmitch/stepFMR/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/jacksonmitch/stepFMR/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

Finite Mixture Regression models allows relationships between the response ($\mathbf{Y}$) and the predictors $(\mathbf{X}_1,\dots, \mathbf{X}_p)$ to differ between a finite number of subpopulations. An R package, stepFMR implements stepwise procedures that select predictors having an effect on the response and determines whether each of the selected predictors has homogeneous or heterogeneous effects. The stepwise procedures are based on hypothesis testing where a weighted significance test (WEST) is used. In mixture regression, 
the unknown number of the subpopulations $G$ (referred as order of the mixture), poses challenges in testing the association between a predictor and the 
response. With WEST, the significance of a predictor's effects on $y$ is the weighted sum of the significance level of all candidate $G$'s. The package supports the Gaussian, Poisson, and Binomial distribution families, and returns the effect types of each predictor, estimate of their effects, as well as the best-fitting $G$.

## Installation

You can install the development version of stepFMR from
[GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("jacksonmitch/stepFMR")
```

## Example

These are basic examples of the function `stepFMR` being used with different distributions, showcasing the different s3 methods to be used with the result:

```{r gaussian}
library(stepFMR)

sim <- fmr_gaussian_example

fit <- stepFMR(sim$formula, sim$data, G_max = 3)
print(fit)
# Align fitted components to the known true groups
aligned <- match_groups(fit, sim$true_group)
aligned$best_fit$parameter_values[["beta_g"]]
```

```{r poisson}
# Poisson
sim_pois <- fmr_poisson_example
fit_pois <- stepFMR(sim_pois$formula, sim_pois$data, G_max = 3, family = "poisson")
summary(fit_pois)
```

```{r binomial}
# Binomial (25 trials per observation)
sim_bin <- fmr_binomial_example
fit_bin <- stepFMR(sim_bin$formula, sim_bin$data, G_max = 3, family = "binomial")
print_steps(fit_bin$variable_selection)
print_steps(fit_bin$effect_determination)
print(fit_bin)
```

